Resolvable Ambiguity

### 2019-07-08 paper/paper.tex
Fix double subscript

\begin{description}
\item[$\dfa(l)$:] Given the production $N -> l : r$, compute the regular language $L' := L(r) \setminus \{N'_m \mid N' \in \NT, m \subseteq \Labels\}$. Then replace every marked non-terminal $N'_m$ with the regular expression $l_1_{l_1 \in m} + l_2_{l_2 \in m} + \ldots + l_n_{l_n \in m}$, where $l_i$ are all the labels of productions $N' -> l_i : r_i$, e.g., $E_{\{a\}}$ in the running example would be replaced by $l_\bot + a_\top + m_\bot + n_\bot$. Then construct a DFA for this language.

>>>>

\begin{description}
\item[$\dfa(l)$:] Given the production $N -> l : r$, compute the regular language $L' := L(r) \setminus \{N'_m \mid N' \in \NT, m \subseteq \Labels\}$. Then replace every marked non-terminal $N'_m$ with the regular expression $l_{1l_1 \in m} + l_{2l_2 \in m} + \ldots + l_{nl_n \in m}$, where $l_i$ are all the labels of productions $N' -> l_i : r_i$, e.g., $E_{\{a\}}$ in the running example would be replaced by $l_\bot + a_\top + m_\bot + n_\bot$. Then construct a DFA for this language.
